\documentclass[a4paper]{journal}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{array}
\usepackage{longtable}

\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand{\thesubsubsection}{\thesubsection.\alph{subsubsection}}

\title{Week 5-11 Research Plan}
\author{Juan Sebastian Martinez Carvajal}
\date{}

\begin{document}
\maketitle
\hrulefill

\section{Meeting Questions and Discussion Items}


\subsection{Research Progress and Major Difficulties}

The progress of the research is accurate with the initial planning and the schedule is being followed correctly. We have made progress in the theoretical background of the research and the tool creation will start this week. Up to this point, no major difficulties have been encountered and the only artifact required to continue our work is the Python source code to be used in the tool, this code was provided recently by my mentors and we can continue making progress.

\subsection{Communication and Documentation of Research Progress}

Up to this point, documentation and communication of the research has been made through an IPython notebook. This mechanism has been successful and no changes were suggested.

\subsection{Meetings with Mentors}

Up to this point, two meetings were held every week where we discussed progress on the research and its theoretical background. These meetings have been very useful and because of this, a good understanding of the project has been accomplished.

\subsection{Research Project Objectives Worksheet}

\begin{longtable}{| m{.2\textwidth} | p{.8\textwidth}|}
  \hline
  \textbf{Week 5} & \\ June 20-24 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Draft an abstract appropriate for a journal article or conference paper
                                      \item Write the ``Introduction" section of your technical paper. Will likely include your literature review (depending on format used).
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Implement version 1.0 of Rappture Tool.
                                      \item Lecture and understanding of information acquisition functions (IAF).
                                    \end{itemize}\\
  \hline
  \textbf{Week 6} & \\ June 27-July 1 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Complete a draft of your technical paper for the Peer-Review Workshop (Thursday, 6/30) by writing the Abstract, Introduction, Methods, and References sections in the style and format of a professional technical conference or journal paper in your field.
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Build version 2.0 of Rappture Tool.
                                    \end{itemize}\\
  \hline
  \textbf{Week 7} & \\ July 4-8 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Complete the first draft of your technical paper with feedback from your mentors and the peer review workshop incorporated into your draft.
                                      \item Determine how to construct your symposium presentation. (How will the flow of the story will go?)
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Complete first draft of technical paper.
                                      \item Start planning of poster and oral presentation.
                                    \end{itemize}\\
  \hline
  \textbf{Week 8} & \\ July 11-15 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Create a draft of your oral presentation slides or poster.
                                      \item Establish a plan for wrapping up your summer research.
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Progress on poster and oral presentation.
                                    \end{itemize}\\
  \hline
  \textbf{Week 9} & \\ July 18-22 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Finalize your abstract and, with professor’s approval, upload to Purdue e-Pubs.
                                      \item Identify the next steps (after SURF) that will allow you to pursue your research interests.
                                      \item Continue to write your final technical paper (Results, Discussion, and Conclusion sections).
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Progress on poster and oral presentation.
                                    \end{itemize}\\
  \hline
  \textbf{Week 10} & \\ July 25-29 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Finalize research presentation (poster or oral) for Symposium, and PRACTICE! [Posters must be printed by Friday of this week.]
                                      \item Continue to prepare your final technical paper.
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Finalize uploading the tool to nanoHub.
                                    \end{itemize}\\
  \hline
  \textbf{Week 11} & \\ August 1-5 &  \textbf{SURF Goals:}
                                    \begin{itemize}
                                      \item Present your research at the SURF Research Symposium on August 4.
                                      \item Wrap up SURF requirements.
                                      \item Update final abstract and technical paper with work done in Week 11.
                                      \item Submit final draft of technical paper to SURF and your lab mentors.
                                      \item Add SURF experience to your resume.
                                      \item Check-out of your lab.
                                    \end{itemize}
                                    \textbf{Research Goals:}
                                    \begin{itemize}
                                      \item Presentation of results and finalize all artifacts.
                                    \end{itemize}\\
  \hline
\end{longtable}

\subsection{Career Goals Discussion}

For my future, I plan to attend graduate school and follow an academic career. With this purpose in mind, my mentors suggested me to start looking for research areas and Professors I woul like to work with. They told me that rather focusing on finding a famous school or a school with a big reputation, I should focus on looking for an advisor that works on research areas that I want. This was said because, in general, Universities have a very good quality, so the biggest criteria to make the decission is the Professor to work with and the research areas he or she focuses on.

\subsection{Format for SURF Symposium Presentation}
\subsubsection{Type of Presentation Suggested by Professor}
\subsubsection{Preferred type of Presentation}
\subsubsection{Title of the Project}
\subsubsection{Keywords for the Project}
\subsubsection{Research Area Theme}
\subsection{Format Used for the Project's Technical Paper}
\end{document}
